\documentclass[twoside,12pt]{article}

\usepackage{dsctemplate}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb,amsthm}
\usepackage{fancyhdr}
\usepackage{nicefrac}
\usepackage{minted}
\usetikzlibrary{quotes,angles,positioning,arrows.meta}
\usetikzlibrary{calc}
\usepackage{enumitem}
\usepackage{fancyvrb}
\usepackage{dirtytalk}
\usepackage{comment}

\DefineVerbatimEnvironment{verbatim}{Verbatim}{xleftmargin=.5in}

% configuration
% ----------------------------------------------https://www.overleaf.com/project/65a60c6c6d7cf6b99f9607b4--------------------------------

% control whether solutions are shown or hidden
\showsolntrue

% page headers only on odd pages
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO]{PID: \rule{3in}{.5pt}}
\renewcommand{\headrulewidth}{0pt}
% \pagenumbering{gobble}

% ------------------------------------------------------------------------------

\begin{document}


\thispagestyle{empty}

\vspace{-5.5in}

\pstitle{%
    Quiz 4
}{DSC 10, Spring 2025}

\vspace{-.3in}

\begin{tabular}{rl}
    Full Name: & \inlineresponsebox[4in]{Solutions}\\
    PID: & \inlineresponsebox[4in]{A12345678}\vspace{.1in}\\
    Quiz Time: & \bubble{3PM} \bubble{3:30PM} \bubble{4PM} \bubble{4:30PM} \vspace{.3in} \\ 
\end{tabular}

\vspace{.1in}

\hline

\vspace{.1in}

\textbf{Instructions:}
    \begin{itemize}
        \item This quiz consists of 3 questions. You have a total of 20 minutes to complete it.
        \item Please write \textbf{clearly} in the provided answer boxes; we will not grade work that appears elsewhere. Completely fill in bubbles and square boxes; if we cannot tell which option(s) you selected, you may lose points.
        
            \bubble{A bubble means that you should only \textbf{select one choice}.}
            
            \squarebubble{A square box means you should \textbf{select all that apply}.}
        \item If your answer is a string, make sure to put it in quotes. If your answer is a float, make sure to include a decimal point.
        \item You may use one handwritten sheet of notes. No calculators and no computers.
    \end{itemize}

\vspace{.1in}

\hline

\vspace{2in}

\noindent By signing below, you are agreeing that you will behave honestly and fairly during
and after this quiz. 

\begin{tabular}{rl}
    \: \: \: \: \: Signature: & \inlineresponsebox[4in]{}\\
\end{tabular}

\vfill

\begin{center}
{\huge Version A} \vspace{.2in}

Please do not open your quiz until instructed to do so.

\end{center}

\newpage

\begin{probset}

\begin{prob}

You want to test the following hypotheses:

\medskip
\textbf{Null Hypothesis:} Everyone who applies for an internship at Google has \textbf{a 20\% chance} of receiving a job offer, independently of all other applicants.

\smallskip
\textbf{Alternative Hypothesis:} Everyone who applies for an internship at Google has \textbf{a more than 20\% chance} of receiving a job offer, independently of all other applicants.

\medskip
To test these hypotheses, you collected information from 50 applicants and found that 16 of them received a job offer.

\begin{subprobset}
    \begin{subprob} Fill in the blanks in the code below to calculate the p-value for a hypothesis test where the test statistic is the number of applicants, out of 50, who receive a job offer.
    \begin{verbatim}
offers_array = np.array([])

for i in np.arange(10000):
    num_offers = ___(a)___
    offers_array = ___(b)___

p_value = ___(c)___
p_value
    \end{verbatim}

    \medskip
    \texttt{(a)}: \inlineresponsebox[5.8in]{\texttt{np.random.multinomial(50, [0.2, 0.8])[0]} or \texttt{np.random.choice([0,1], 50, p = [0.80, 0.20]).sum()}}
    \texttt{(b)}: \inlineresponsebox[5.8in]{\texttt{np.append(offers\_array, num\_offers)}}
    \texttt{(c)}: \inlineresponsebox[5.8in]{\texttt{np.count\_nonzero(offers\_array >= 16)/10000} or \texttt{np.mean(offers\_array >= 16)}}
    \end{subprob}

    \begin{subprob}
    Suppose the p-value comes out to $0.03$. What conclusion do we draw?

    \smallskip
    
    \bubble{We reject the null hypothesis at both the $0.01$ and $0.05$ significance levels.} 

    \smallskip
    
    \correctbubble{We fail to reject the null hypothesis at the $0.01$ significance level and we reject the\\ \hspace*{1.2em} null hypothesis at the $0.05$ significance level.}

    \smallskip

    \bubble{We reject the null hypothesis at the $0.01$ significance level and we fail to reject the\\ \hspace*{1.2em} null hypothesis at the $0.05$ significance level.}

    \smallskip
    
    \bubble{We fail to reject the null hypothesis at both the $0.01$ and $0.05$ significance levels.}
    
    \end{subprob}
    \newpage
    \begin{subprob}
        Which of the following test statistics would have also been appropriate to test these hypotheses? Select all that apply.

        \smallskip

        \correctsquarebubble{Number of applicants, out of 50, who do not receive a job offer.} 

        \smallskip
        
        \correctsquarebubble{Proportion of applicants that receive a job offer.}
    
        \smallskip
    
        \squarebubble{The sum of the absolute differences between $[0.2, 0.8]$ and the distribution of\\ \hspace*{1.2em} applicants into two categories: those getting a job offer and those not getting a job\\ \hspace*{1.2em} offer.}
    
        \smallskip
        
        \squarebubble{Absolute difference between 20 and the number of applicants, out of 50, who receive\\ \hspace*{1.2em} a job offer.}

        \smallskip
        
        \squarebubble{None of the above.}
    
    \end{subprob}
\end{subprobset}

\end{prob}

\bigskip

\begin{prob}

According to Indeed, a popular job website, the hourly pay for data science interns across the US has a mean of 24 and a standard deviation of 6. You take a random sample of 64 data science interns. In your sample, the hourly pay has a mean of 25 and a standard deviation of 4. Suppose you bootstrap your sample 10,000 times, calculate the mean hourly pay from each resample, and plot a histogram of these resampled means. Which of the following best describes this histogram?

\bubble {Roughly normal with a mean of 24 and a standard deviation of 6.}

\smallskip

\bubble{Roughly normal with a mean of 24 and a standard deviation of 0.75.}

\smallskip

\bubble{Roughly normal with a mean of 25 and a standard deviation of 4.}

\smallskip

\correctbubble{Roughly normal with a mean of 25 and a standard deviation of 0.5.}

\smallskip

\bubble{None of the above.}

\end{prob}

\bigskip

\begin{prob}
You are interested in estimating the average wait time between an interview and an internship offer being made. You take a random sample of $n$ internship offers and find that in this sample, the average wait time is $d$ days and the standard deviation is 4 days. 

You construct a 95\% CLT-based confidence interval for the true average wait time, in days, which comes out to $[10.4, 13.6]$. Find $n$ and $d$.

    \begin{center}  
    \text{$n$ =} \inlineresponsebox[1.5in]{\texttt{25}}{} 
    \hspace{0.5in}
    \text{$d$ =} \inlineresponsebox[1.5in]{\texttt{12}}{}  
    \end{center}
    
\end{prob}
\end{probset}


\newpage

\begin{center}
\textbf{Reminders:}
\begin{itemize}
    \item \textbf{Write your PID} on the front page and on the top right corner of page 3.
    \item If your answer is a string, make sure to put it in \textbf{quotes}.
    \item If your answer is a float, make sure to include a \textbf{decimal point}.
    \item Stay in your seat until the quiz is over. No leaving early.
\end{itemize}
\end{center}

\end{document}
